The impact of gas bulk rotation on the Lyman $\alpha$ line

### 2014-07-07 paper/ms.tex
new caption figure 9

\begin{figure*}
\begin{center}
    \includegraphics[width=0.45\textwidth]{f12.pdf}
    \includegraphics[width=0.45\textwidth]{f13.pdf}
\end{center}
\caption{Logarithm of the average number of scatterings as function of
  $\mu$ (left panel) and the maximum rotational velocity $V_{\rm
max}$. The left panel shows the behaviour for $\tau=10^{5}$ and
  $V_{max}=300$\kms as a function of $|\cos\theta|$; the independence of
  $N_{\rm scatt}$ with $\mu$ is present in all models.
  In the right panel the continuous (dashed) lines represent an
  central (homogeneous) distribution of sources; there is a clear
  decrease in the number of scatterings for the homogeneously
  distributed sources.
\label{fig:Nscatt} }
\end{figure*}

%\begin{figure*}
%\begin{center}
%  \includegraphics[width=0.48\textwidth]{f14_1.pdf}
%  \includegraphics[width=0.48\textwidth]{f14_2.pdf}
%  \includegraphics[width=0.48\textwidth]{f14_3.pdf}
%  \includegraphics[width=0.48\textwidth]{f14_4.pdf}    
%\end{center}
%    \caption{2D histogram of $N_{\rm scatt}$ vs $x$. The upper (lower) panels
%      show the homogeneous (central) source distribution. Left panels 
%      corresponds to the static case and right panels correspond to
%      $V_{\rm max}=300\kms$. The color scale is logarithmic on the
%      number of photons with given values of $N_{\rm scatt}$ and
%      $x$. \label{fig:Nscatt2D}. }
%\end{figure*}

>>>>

\begin{figure*}
\begin{center}
    \includegraphics[width=0.45\textwidth]{f12.pdf}
    \includegraphics[width=0.45\textwidth]{f13.pdf}
\end{center}
\caption{Logarithm of the average number of scatterings as function of
  $\mu$ (left) and the maximum rotational velocity $V_{\rm
max}$ (right). The left panel shows the behaviour for $\tau=10^{5}$ and
  $V_{max}=300$\kms as a function of $\left|\cos\theta\right|$; the independence of $N_{\rm scatt}$ with $\mu$ and $V_{\rm max}$ is present in all models.
\label{fig:Nscatt} }
\end{figure*}
